### 2019-03-29 5_evaluation.tex
Tweak text.

Implicitly parallel systems, such as PaRSEC, StarPU, and Regent, that
perform runtime analysis in order to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially be allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG provides some
improvement over DTD by performing DAG expansion at compile time, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC DTD Shard.

>>>>

Implicitly parallel systems such as PaRSEC, StarPU and Regent that
rely on runtime analysis to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes and thus limits scalability. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD by performing DAG expansion at compile time, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC DTD Shard.
